A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
added cn2 description to slides.
fixing presentation footer.

\urldef{\mails}\path|ei05011@fe.up.pt,ei05028@fe.up.pt|
\title[A comparison of classification algorithms applied to the Adult Database \insertframenumber/\inserttotalframenumber]{A comparison of classification algorithms applied to the Adult Database}
\author{Flávio Cruz and João Azevedo}
\institute{Faculdade de Engenharia da Universidade do Porto\\
\mails}
\date{\today}

@@

\subsection{Rule Induction}
\frame
{
}

>>>>

\urldef{\mails}\path|ei05011@fe.up.pt,ei05028@fe.up.pt|
\title[Classification on the Adult Database \insertframenumber/\inserttotalframenumber]{A comparison of classification algorithms applied to the Adult Database}
\author{Flávio Cruz and João Azevedo}
\institute{Faculdade de Engenharia da Universidade do Porto\\
\mails}
\date{\today}

@@

\subsection{Rule Induction}
\frame
{
    \frametitle{Rule Induction}

    \begin{itemize}
    \item<1-> Peter Clark's CN2 software was used to induce rules:
    \begin{itemize}
        \item<1-> \url{http://www.cs.utexas.edu/users/pclark/software/\#cn2}.
    \end{itemize}
    \item<1-> CN2 can generate both ordered and unordered set of rules.
    \item<1-> Peter Clark's software can use different error estimations:
    \begin{itemize}
        \item<1-> Laplacian.
        \item<1-> Naive.
        \item<1-> Information Gain.
        \item<1-> Modified Entropy.
    \end{itemize}
    \end{itemize}
}
